\renewcommand{\Chapter}{{Acknowledgements}}
\chapter*{\Chapter}
\chaptermark{\Chapter}
\addcontentsline{toc}{chapter}{\Chapter}

I want to thank my supervisor, \textbf{Antonio Ereditato}, for making this thesis possible.
In particular, you have supported my decision to write a hardware thesis.
This probably would not have been possible at many other institutions.

I would like to express my gratitude to my examiners \textbf{Hucheng Chen} and \textbf{Peter Wurz}.

Some of my most sincere praise goes to \textbf{Igor Kreslo}.
You taught me most of my detector physics knowledge and (almost) always had an answer to my questions.
It was always enlightening and a great pleasure to discuss with you and to be challenged by you.

I also want to thank \textbf{Michele Weber} for the many times he provided me with a simple solution to a seemingly complex problem, be it physical or organisational.

I am really grateful to \textbf{James Sinclair} for his guidance, in particular, towards the end of my thesis.
More than once, you prevented me from despairing or accidentally killing myself in the lab.
Surprisingly, you never got tired of reading my thesis and fixing my abominations of the English language.

The collaboration with \textbf{Christoph Urs Benjamin Rudolf von Rohr}, \textbf{David \gls{lorca}}, \textbf{Francesca Stocker}, \textbf{Martin Auger}, \textbf{Matthias Lüthi}, and \textbf{Yifan Chen} from the \gls{help} \lar{} group was simply outstanding.
Thank you very much for the countless hours spent together in the lab, office, and, most importantly, pub.

Without the input of \textbf{Tracy Usher} and \textbf{Yun-Tse Tsai} from SLAC, I would not have succeeded at reconstructing the pixel data.
Thank you!

A very big thank you to \textbf{Dean Shooltz} from \lariat{} for providing the documentation of the differential warm signal path of \lariat{}.
This allowed me to tame our setup haunted by noise.

I am grateful to \textbf{Emerson Vernon}, \textbf{Gianluigi De Geronimo}, \textbf{Hucheng Chen}, \textbf{Jack Fried}, \textbf{Linda Feierabend}, \textbf{Neena Nambiar}, and \textbf{Shanshan Gao} for the great time I had at \gls{bnl} and everything they taught me about electronics.
I really enjoyed the company of \textbf{Aseem Gupta}, \textbf{Hannah Herde}, and \textbf{Stefania Stucci}.

I want to thank \textbf{Kam-Biu Luk} and the neutrino group at \gls{lbnl} for hosting me.
In particular, I am grateful to \textbf{Daniel Dwyer} for telling me everything about \larpix{}, and \textbf{Chris Marshall} for his guidance on the \gls{nd} pile-up study.

None of this would have been possible without the excellent support of \textbf{Camilla Tognina} and \textbf{Pascal Lutz} from the \gls{help} electronics workshop; as well as \textbf{Roger Hänni}, \textbf{Jan Christen}, \textbf{Lorenzo Meier}, \textbf{Gregor Pfäffli}, and \textbf{Roger Liechti} from the \gls{help} mechanical workshop.
Thank you!

I am really thankful to all the other friends I have made at \gls{help} for the magnificent time: \textbf{Callum Wilkinson}, \textbf{Daniel Coderre}, \textbf{Lukas Bütikofer}, \textbf{Marcel Häberli}, \textbf{Martin Hierholzer}, \textbf{Martti Nirkko}, \textbf{Razvan Gornea}, \textbf{Sabina Joos}, and \textbf{Sébastien Delaquis}.

Furthermore, I am grateful to \textbf{Ursula Witschi}, \textbf{Marcella Esposito}, and \textbf{Irene Neeser} from the \gls{help} secretariat for their patience with my inferior organisation.

I also appreciate the computing support from \textbf{Jeremy Singh}, \textbf{Gianfranco Sciacca}, and \textbf{Luis Martinez}.

I am thankful to \textbf{Luke Pickering} from \gls{msu} for generating a custom flux cross-section plot for me.

I would like to express my gratitude to the \gls{snf} and ultimately Swiss tax payers for paying me for what I like to do.

This research used resources of the \gls{nersc}, a \gls{doe} Office of Science User Facility supported by the Office of Science of \gls{doe} under Contract No.\ DE-AC02-05CH11231.

My warmest thanks go to all my friends for their continued support even though I neglected them more than once during the last four years.

I am most grateful to my flatmate, \textbf{Annette Mettler}, and her husband, \textbf{Raphaël Guillet}, for bearing with me for the last years.
You have become like family to me.

Most of all, I want to thank my parents, \textbf{Brigitte} and \textbf{Willi Göldi}, and my brother, \textbf{Sebastian Göldi}, for their (moral and financial) support.
You taught me the most important lesson in science (and maybe also life): Always stay curious and question everything.