\chapter{Conclusion}
\label{chap:conclusion}

\dune{}, a planned long-baseline neutrino oscillation experiment, aims to discover CP violation and determine the neutrino mass ordering.
Due to its excellent tracking and calorimetry, a \lartpc{} will be deployed for the far detector.
To bring systematic uncertainties down to an acceptable level, a near detector \lartpc{} component is required.
This environment will be very challenging due to the slow nature of \lartpc{}s compare to the beam pulse duration.
The high beam intensity will therefore lead to significant event pile-up.

In this thesis, all relevant challenges for such a near detector \lartpc{} were studied, namely the dielectric strength of \lar{}, new charge and light readout methods, as well as the required next-generation readout electronics.
After the \AT{} experiment at the University of Bern had suffered from serious HV problems, a systematic study of dielectric breakdowns in \lar{} was undertaken.
In particular, it was found that the dielectric strength is dependent on absolute dimensions.
High-speed footage, current-voltage characteristics, and spectrometry of breakdowns were recorded.
From this, a conclusive theory of dielectric breakdowns in \lar{} at the centimetre scale was developed.
The phenomenon is governed by three distinct phases: field emission, streamer, and breakdown.
Understanding the process enabled the development of a technique to mitigate the breakdowns.
This can be achieved by coating exposed high-voltage parts with a slightly conducting polymer layer (latex in our case).
While the uncoated tests indicated a maximum safe field of only \SI{40}{\kilo\volt\per\centi\metre} (as opposed to $\approx \SI{1}{\mega\volt\per\centi\metre}$ predicted by studies in the fifties), with coating, an improvement of an order of magnitude was reached.
However, this solution proved to be unreliable.
The latex layer is very sensitive and can easily be damaged, rendering its protective property defunct.
Additionally, its behaviour under multiple thermo-cycles is not yet fully understood.
Therefore, polymer coating is not suitable for large physics experiments and the only solution is to keep fields below \SI{40}{\kilo\volt\per\centi\metre} everywhere in the detector.

Classical wire plane readouts of \lartpc{} have significant drawbacks.
Besides their mechanical fragility, they cripple the excellent 3D tracking capabilities of a TPC by reducing it two multiple 2D projections.
This is highly problematic in high-multiplicity environments such as the \dune{} near detector.
In a preliminary study, it was shown that the mechanical challenges can be alleviated by replacing the wires with copper tracks printed on a thin Kapton layer.
However, this does not solve the ambiguities.
For this, a true 2D readout in form of pixels is needed.
Realising a pixelated \lartpc{} is complicated because of the high number of channels.
Cold digitisation can help out by aggregating many pixels on a single high-speed digital link, reducing the number of required cable feedthroughs out of the cryostat.
The cold digitisers foreseen for the \dune{} far detector were evaluated and found unsuitable for a pixelated near detector.
Being optimised for wire readouts, their power dissipation is much too high given the required number of channels.
With no suitable cold electronics at hand, a form of analogue multiplexing had to be implemented to demonstrate a pixelated \lartpc{}.
This was achieved by dividing the pixel readout into regions of interest with pixels of different regions sharing the same digitiser channel.
To disentangle the correct physical pixel, each region is surrounded by an inductive grid.
Combining the inductive pulses with the collected charge, it is possible to derive the true position.
Like this, it was possible to use the existing charge readout electronics from ARGONTUBE.
However, this scheme introduces a certain amount of ambiguity.

A new prototype TPC was designed and built to test the pixelated charge readout scheme.
Besides, it was also used to test the operation of SiPMs in \lar{} for the light trigger system.
Several thousand cosmic muon tracks were recorded in two measurement campaigns.
The first measurement campaign suffered from high noise levels on the charge readout.
Subsequently, the ARGONTUBE readout electronics were extended by a differential warm signal path, and the parasitic capacitances in the pixel readout PCB were reduced.
In the second run, a SNR of \num{14} on the pixel channels could be reached, proving a sufficient performance of pixels for operation in a real physics experiment.
These results triggered the development of bespoke cold pixel electronics, \larpix{}, by LBNL, aimed to eventually enable an ambiguity-free pixelated \lartpc{} charge readout.

To reconstruct the cosmic muon tracks, a new software framework was developed.
The hit finder had to be written from scratch because all existing \lartpc{} reconstruction frameworks are optimised for wire readouts.
A principal components analysis was employed to solve the ambiguities stemming from the analogue multiplexing.
Finally, the unambiguous 3D measurements were fed to GENFIT, an existing generic track-fitting toolkit based on a Kalman filter.
Therewith, fully reconstructed cosmic muon tracks were obtained.

The work is concluded by an event pile-up study of the \dune{} near detector using \Pgpz decay photons.
At \dune{} energies, these photons produce EM showers consisting of a plethora of small disconnected charge depositions in the detector.
Correctly associating these to the right neutrino event is one of the most difficult reconstruction tasks.
At the same time, failure to reconstruct them properly, significantly impedes the reconstructed neutrino energy spectrum.
Based on the results from the pixel prototype test, unambiguous 3D position information for the charge depositions was assumed.
A simple cone-based algorithm was employed to associate the charge to the corresponding photon.
The algorithm was found to miss less than \SI{3}{\percent} of the deposited energy on average.
More importantly, the pile-up-related misidentification of energy depositions from other events was found to be \SIrange{2}{3}{\percent} on average.
For more than \SI{50}{\percent} of the neutrino events, this error is even smaller than \SI{0.1}{\percent}.

The combination of all the results from this work builds the groundwork for the \AC{}, a novel, fully modular \lartpc{} concept, addressing the most important challenges of future neutrino detectors, in particular the \dune{} near detector.
High cathode voltages are prevented by splitting the detector into several small, self-contained TPCs requiring only a moderate \SI{50}{\kilo\volt} cathode voltage.
A pixelated readout enables the true 3D tracking required to cope with the high event rates resulting from the high-intensity neutrino beam.
The \AL{} light readout minimises the dead volume in between the modules, resulting in a similar performance to a monolithic detector while containing the scintillation light within the modules, simplifying association to the correct ionisation signals.
Due to these properties, \AC{} is the top candidate for the \lar{} component of the \dune{} near detector.
